Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
project actually started in 2007

Started in 2009, \sklearn is developed by an international team of a dozen of
core developers, mostly researchers from various fields (e.g., machine learning,
natural language processing, or neuroscience). The project also greatly benefits
from many occasional contributors proposing small code or documentation fixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
In addition, complete documentation and examples are required for all features.
Finally, additions to the code base must pass code review by at least two
developers not involved in the implementation of the proposed addition.

>>>>

Started in 2007, \sklearn is developed by an international team of a dozen of
core developers, mostly researchers from various fields (e.g., machine learning,
natural language processing, or neuroscience). The project also greatly benefits
from many occasional contributors proposing small code or documentation fixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
In addition, complete documentation and examples are required for all features.
Finally, additions to the code base must pass code review by at least two
developers not involved in the implementation of the proposed addition.
